---
title: "Tidy Tuesday on Wednesday"
subtitle: "www.inqs.info/ttw"
date: 02-20-25
description: Tidy Tuesday on Thursday at CSUCI! Analyzing Agencies from the FBI Crime Data API!
format:
  revealjs:
    scrollable: true
    navigation-mode: vertical
    controls-layout: bottom-right
    controls-tutorial: true
    incremental: false 
engine: knitr
knitr:
  opts_chunk: 
    echo: true
    eval: false
    comment: "#>" 
draft: false
categories:
  - sp2025
execute: 
  cache: true
---

# Tidy Tuesday

## Tidy Tuesday

[Tidy Tuesday](https://tidytues.day/) is a weekly data visualization challenge from the [Data Science Learning Community](https://dslc.io/).

## Week 7, 2025

::: panel-tabset

### Info

More information about the data can be found on [GitHub](https://github.com/rfordatascience/tidytuesday/blob/main/data/2025/2025-02-18/readme.md).

### CSV

[DATA](https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-02-18/agencies.csv)



### R Code

```{r}
#| echo: true
#| eval: true

tuesdata <- tidytuesdayR::tt_load(2025, week = 7)

agencies <- tuesdata$agencies

```

### Data

```{r}
#| eval: true
#| echo: false
agencies |> DT::datatable(options = list(pageLength = 1, dom = "tp"))

```

:::

## R Softare

[R](https://www.r-project.org/): R is a statistical programming package that allows you to conduct different types of analysis.

[RStudio](https://posit.co/downloads/): A piece of software that organizes how you conduct statistical analysis in R.

[Posit Cloud](https://posit.cloud/login): A web version of RStudio.

## Recommended R Packages

::: panel-tabset

### General

```{r}
#| echo: true
#| eval: false

install.packages("tidyverse")
install.packages("plotly")
install.packages("ggwordcloud")
install.packages("ggthemes")
install.packages("ggpie")
install.packages("ggbump")
install.packages("tidytext")
install.packages("remotes")
install.packages("esquisse")
install.packages("tidytuesdayR")
remotes::install_github("MatthewBJane/ThemePark")

```


### Spatial

```{r}
#| echo: true
#| eval: false

install.packages("sf")
install.packages("terra")
install.packages("spData")
install.packages("spDataLarge", repos = "https://geocompr.r-universe.dev")
```

:::


## Visualization Resources

[R Graphics Cookbook](https://r-graphics.org/)

[R Graph Gallery](https://r-graph-gallery.com/)

[R Charts](https://r-charts.com/)

[ggplot2](https://ggplot2.tidyverse.org/)

[Spatial Data Science](https://r-spatial.org/book/)

[Spatial Data Analysis](https://paezha.github.io/spatial-analysis-r/)

[Geocomputation in R](https://r.geocompx.org/)

## Tidy Tuesday Community Examples

[poncest](https://github.com/poncest/tidytuesday/tree/main/2024/Week_09)

[project_presentations](https://github.com/Aditya-Dahiya/projects_presentations/blob/main/projects/tidy_leap_day.R)

[mvbloois](https://github.com/mvbloois/tidytuesday/tree/main/2024/2024-02-27)

# Example 1

## Example 1

Create a density map of all the agencies located in 
